Project Description -- Erosion, Transport, Anomalous Diffusion, and Collapse in Granular and Porous Media

### 2019-11-11 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

%---------------------------------------------------------------------------------------------------%
%% TITLE
\begin{document}
\title{Project Description --
CAREER: Erosion, Seepage, Transport, and Collapse in Granular and Porous Media}

@@

The $j^{th}$ trajectories, or characteristics, is governed by
$\dot{ss}_j(t) = \uu(\ss_j(t))$. Once these trajectories are computed,
using, for example, a high-order Runge-Kutta method, a statistical
analysis be used to describe the transport. Two of the most important
measurements are the tortuosity and the anomalous dispersion, both which
are defined in terms of the length of the trajectories
\begin{align}
  \lambda_j(t) = \int_{0}^{t} \|\ss'(t')\| dt'.
\end{align}
Once $N_p$ trajectories are computed, the tortuosity is the
dimensionless number
\begin{align}
  T = \frac{1}{d} \left(\int_{S} u_1(x_0,y_0)\lambda(y_0) dy_0\, \right)
  \Bigg/ \left(\int_S u_1(x_0,y_0)\, dy_0 \right),
\end{align}
where $S$ is the vertical cross-section at $x=x_0$, $d$ is its length,
$u_1$ is the horizontal velocity, and $\lambda(y_0)$ is the length of
the trajectory starting at $(x_0,y_0)$ and ending at a vertical
cross-section at the other end of the channel. Relationships between the
tortuosity and porosity of a geometry have been developed by other
groups~\cite{kop-kat-tim1996, dud-koz-mat2011, mat-kha-koz2008}, and
preliminary results indicate that such models might be appropriate for
geometries whose porosity is increasing under the process of erosion
(Figure~\ref{fig:100tortuosity}).

>>>>

%---------------------------------------------------------------------------------------------------%
%% TITLE
\begin{document}
\title{Project Description --
Erosion, Transport, Anomalous Diffusion, and Collapse in Granular and Porous Media}

@@

The $j^{th}$ trajectories, or characteristics, is governed by
$\dot{\ss}_j(t) = \uu(\ss_j(t))$. Once these trajectories are computed,
using, for example, a high-order Runge-Kutta method, a statistical
analysis be used to describe the transport. Two of the most important
measurements are the tortuosity and the anomalous dispersion, both which
are defined in terms of the length of the trajectories
\begin{align}
  \lambda_j(t) = \int_{0}^{t} \|\ss'(t')\| dt'.
\end{align}
Once $N_p$ trajectories are computed, the tortuosity is the
dimensionless number
\begin{align}
  T = \frac{1}{d} \left(\int_{S} u_1(x_0,y_0)\lambda(y_0) dy_0\, \right)
  \Bigg/ \left(\int_S u_1(x_0,y_0)\, dy_0 \right),
\end{align}
where $S$ is the vertical cross-section at $x=x_0$, $d$ is its length,
$u_1$ is the horizontal velocity, and $\lambda(y_0)$ is the length of
the trajectory starting at $(x_0,y_0)$ and ending at a vertical
cross-section at the other end of the channel. Relationships between the
tortuosity and porosity of a geometry have been developed by other
groups~\cite{kop-kat-tim1996, dud-koz-mat2011, mat-kha-koz2008}, and
preliminary results indicate that such models might be appropriate for
geometries whose porosity is increasing under the process of erosion
(Figure~\ref{fig:100tortuosity}).
